Proving linearizability using forward simulations\thanks{An extended version of this paper including the missing proofs can be found at \cite{extended}.}

### 2017-05-08 draftCAV/stack.tex
TSS simulation

Note that $F_2$ cannot satisfy the reverse of {\bf \emph{Frontiers}}, i.e., every push in $\mathsf{overlap}(p) \cup \mathsf{maxAtInvoc}(p)$, for some $p$, is maximal or followed only by pending pushes (w.r.t., $\mathsf{before}$). This is because 
%The dual condition of ensuring maximal-closedness of remove candidate push operations is not valid for $F_2$, since 
the linearization points of pop operations are not fixed and they can occur anywhere in between their invocation and commit points. Hence, any push operation which was maximal or followed only by pending pushes in the happens-before 
%that is maximally-closed 
in between the invocation and the commit 
can be removed by a pop. And such a push may not satisfy the same properties in the state $s$. 
% and they might not be maximally-closed in the current state. Unfortunately, $\mathit{TSS}$ does not keep history of pop operations in the state and we cannot infer all the push operations that are concurrent or maximally closed with respect to a given pop operation from the state information.
%Nevertheless, we can obtain partial information from the state that is enough for showing once-maximality of a push that is removed by commit action of a pop. First, the push operations tht are maximally-closed in the current state are remove candidates by all pending pops since a pending pop operation may linearize at this point. This restriction is described by the \emph{Frontiers} condition.

 To obtain further information on $\mathsf{overlap}$ and $\mathsf{maxAtInvoc}$ sets of a pending pop $p$ in state $s$, we look at $youngest_s(p)$ and $n_s(p)$ which show the current youngest element $p$ has seen and the current element $p$ is visiting, respectively. \emph{TraverseBefore} and \emph{TraverseBeforeNull} conditions make sure that if threads add new nodes to their pools after $p$ passes them during its travels, these pushes must be concurrent with $p$. The \emph{TraverseAfter} condition makes sure that either the current youngest node $youngest_s(p)$ is in $\mathsf{overlap}_s(p) \cup \mathsf{maxAtInvoc}_s(p)$ or there is a future node that $p$ will visit and this future node is in $\mathsf{overlap}_s(p) \cup \mathsf{maxAtInvoc}_s(p)$.

Combining \emph{TraverseBefore} and \emph{TraverseAfter} restrictions we make sure that when a new node $n_s(p)$ is visited, then either $youngest_s(p)$ was maximally-closed before new nodes that precede $n_s(p)$ in the traverse order were added, or there is a successor node of $n_s(p)$ in the traverse order that is maximally-closed. Hence, when $p$ finishes its traversal of pools with a non-null and present $youngest$ node, this node is guaranteed to be once-maximal between invocation and commit points of $p$.

>>>>

Note that $F_2$ cannot satisfy the reverse of {\bf \emph{Frontiers}}, i.e., every push in $\mathsf{overlap}(p) \cup \mathsf{maxAtInvoc}(p)$, for some $p$, is maximal or followed only by pending pushes (w.r.t., $\mathsf{before}$). This is because 
%The dual condition of ensuring maximal-closedness of remove candidate push operations is not valid for $F_2$, since 
the linearization points of pop operations are not fixed and they can occur anywhere in between their invocation and commit points. Hence, any push operation which was maximal or followed only by pending pushes in the happens-before 
%that is maximally-closed 
in between the invocation and the commit 
can be removed by a pop. And such a push may no longer satisfy the same properties in the state $s$.

Based on the values stored in $youngest_s(p)$ and $n_s(p)$, for some pop $p$, %which give the current youngest element $p$ has seen and the current element $p$ is visiting, 
the other three constraints identify other push operations that overlap with $p$, or they were followed only by pending pushes when $p$ was invoked. 
% and they might not be maximally-closed in the current state. Unfortunately, $\mathit{TSS}$ does not keep history of pop operations in the state and we cannot infer all the push operations that are concurrent or maximally closed with respect to a given pop operation from the state information.
%Nevertheless, we can obtain partial information from the state that is enough for showing once-maximality of a push that is removed by commit action of a pop. First, the push operations tht are maximally-closed in the current state are remove candidates by all pending pops since a pending pop operation may linearize at this point. This restriction is described by the \emph{Frontiers} condition. 
%To obtain further information on $\mathsf{overlap}$ and $\mathsf{maxAtInvoc}$ sets of a pending pop $p$ in state $s$, we look at  which show the current youngest element $p$ has seen and the current element $p$ is visiting, respectively. 
{\bf \emph{TraverseBefore}} and {\bf \emph{TraverseBeforeNull}} state that pushes which add new nodes to the pools seen by $p$ in the past,  are overlapping with $p$. {\bf \emph{TraverseAfter}} states that either the push adding the current youngest node $youngest_s(p)$ is in $\mathsf{overlap}_s(p) \cup \mathsf{maxAtInvoc}_s(p)$, or there is a node that $p$ will visit in the future which is in $\mathsf{overlap}_s(p) \cup \mathsf{maxAtInvoc}_s(p)$.

%Combining \emph{TraverseBefore} and \emph{TraverseAfter} restrictions we make sure that when a new node $n_s(p)$ is visited, then either $youngest_s(p)$ was maximal or followed only by pending pushes before new nodes that precede $n_s(p)$ in the traverse order were added, or there is a successor node of $n_s(p)$ in the traverse order that is maximal or followed only by pending pushes. Hence, when a pop $p$ finishes its traversal of the pools with a non-null and present $youngest$ node, this node is guaranteed to be once-maximal between invocation and commit points of $p$.
